Implementing DNS in C0

### 2017-11-17 proposal.tex
clarify
Evaluation section added.

The bulk of this goal falls into the two components described in \S\ref{sec:our-project}, along with a small ``main'' component that uses these to actually handle queries. Currently, we have unmarshalling functions and about a third of the network library implemented. We expect that the remainder of this goal should go fairly quickly --- marshalling is no harder than unmarshalling, and the network interface is relatively straightforward to implement once we have decided on what functions are necessary and what their arguments should be.

@@

Klaas.

>>>>

The bulk of this goal falls into the two components described in \S\ref{sec:our-project}, along with a small ``main'' component that uses these to actually handle queries. Currently, we have some unmarshalling functions and about a third of the network library implemented. We expect that the remainder of this goal should go fairly quickly --- marshalling is no harder than unmarshalling, and the network interface is relatively straightforward to implement once we have decided on what functions are necessary and what their arguments should be.

@@

Our evaluation breaks down into two parts --- one on the safety, and one on performance. As safety is a primary goal of this project, we plan to evaluate our code for safety. A large part of this will come for free from the memory safety guarantees of \Kwd{C0}, with the rest coming from a careful analysis of our \Kwd{C} code. This does have the disadvantage that \Kwd{C0}'s memory safety is checked dynamically, which incurs performance overhead. Ideally, as described in our 125\% goal, we would like to have a more static verification that memory safety holds, both to provide better performance, and as it provides better results than dynamic checking, since if a dynamic check fails, the program halts, which is less than ideal.

For performance analysis, we plan to evaluate our nameserver for latency and throughput, as these appear to be the most important metrics for \Kwd{DNS} performance. We plan to do this using one of two pieces of software\footnote{https://github.com/cobblau/dnsperf, https://github.com/nominum/dnsperf} (confusingly, both named \texttt{dnsperf}), which read queries from a file and then send these requests to a nameserver. The latter seems better-suited to our needs, as the former appears to not give latency information in a useful fashion. We will compare our results (at various load levels) to existing \Kwd{DNS} software (though we have yet to determine which specific software to take as our baseline). One remaining difficulty in evaluation lies in figuring out what sort of query workload to use --- the performance analysis tools we have looked at suggest using an input file with somewhere on the order of one million queries, which is more than can feasibly be generated by hand. However, there does not appear to be a standard benchmark for this testing as there are for many other systems. We will likely generate large test files in a randomized way, but do not have a good sense of how to make these files accurately reflect realistic usage.
